Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-16 paper/main.tex
add note to Wolbers (2011)

% literature review overview 1: imagination & haptic exploration
Increased hemodynamic activity in the PPA generalizes to mental imagination of
landscapes \citep{ocraven2000mental} and haptic exploration of scenes
constructed from LEGO blocks \citep{wolbers2011modality}.\todo{cite Lescroart \&Gallant,
Human Scene-Selective Areas Represent 3D Configurations of Surfaces, Neuron, 2019;
semi-naturalistic, but not taskfree, 800+ stimulus, not "a small set", 6 subjects}
% O'Craven: watching pictures
In a study conducted by \cite{ocraven2000mental} participants viewed alternating
blocks of pictures showing familiar places and famous faces during an initial
experimental paradigm.
% O'Craven: mental imagery
In a subsequent paradigm, participants were instructed to ``form a vivid mental
image'' of the previously viewed pictures.
% O'Craven results
The PPA showed increased activation during imagination of places compared to
faces but the imagination tasks showed a smaller activation level compared to
the perceptual task.
% Wolbers: haptic exploration
In a block design study conducted by \cite{wolbers2011modality} the PPA of
participants showed increased activation during a delayed
match-to-sample task of haptically explored scenes constructed from LEGO bricks
compared to abstract geometric objects.
% Wolbers: connectivity analysis

>>>>

% literature review overview 1: imagination & haptic exploration
Increased hemodynamic activity in the PPA generalizes to mental imagination of
landscapes \citep{ocraven2000mental}, and haptic exploration of scenes
constructed from LEGO blocks \citep{wolbers2011modality}.\todo{cite Lescroart
    \&Gallant, Human Scene-Selective Areas Represent 3D Configurations of
    Surfaces, Neuron, 2019; semi-naturalistic, but not taskfree, 800+ stimulus,
not "a small set", 6 subjects}
% O'Craven: watching pictures
In a study conducted by \cite{ocraven2000mental} participants viewed alternating
blocks of pictures showing familiar places and famous faces during an initial
experimental paradigm.
% O'Craven: mental imagery
In a subsequent paradigm, participants were instructed to ``form a vivid mental
image'' of the previously viewed pictures.
% O'Craven results
The PPA showed increased activation during imagination of places compared to
faces but the imagination tasks showed a smaller activation level compared to
the perceptual task.
% Wolbers: haptic exploration
In a block design study conducted by \cite{wolbers2011modality} the PPA of
sighted as well as blind participants showed increased activation during a
delayed match-to-sample task of haptically explored scenes constructed from LEGO
bricks compared to abstract geometric objects.
% Wolbers: connectivity analysis
